---
title: "Calculating Capital Asset Pricing Model"
author: "Eric Wang"
date: "5 March 2018"
output: html_document
---


The portfolio that I'm going to analysis consists:

>+ SPY (S&P500 fund) weighted 25%
>+ EFA (a non-US equities fund) weighted 25%
>+ IJS (a small-cap value fund) weighted 20%
>+ EEM (an emerging-mkts fund) weighted 20%
>+ AGG (a bond fund) weighted 10%

Then I need to find out the monthly returns of above mentioned portfolio, I copied code from <a href = "https://rviews.rstudio.com/2018/02/08/capm-beta/" title="portfolio monthly return">Monthly return</a>

```{r}
library(tidyquant)
library(tidyverse)
library(timetk)
library(tibbletime)
library(broom)

symbols <- c("SPY","EFA", "IJS", "EEM","AGG")

prices <- 
  getSymbols(symbols, src = 'yahoo', 
             from = "2013-01-01",
             to = "2017-12-31",
             auto.assign = TRUE, warnings = FALSE) %>% 
  map(~Ad(get(.))) %>%
  reduce(merge) %>% 
  `colnames<-`(symbols)

prices_monthly <- to.monthly(prices, indexAt = "last", OHLC = FALSE)

asset_returns_xts <- na.omit(Return.calculate(prices_monthly, method = "log"))

w <- c(0.25, 0.25, 0.20, 0.20, 0.10)

portfolio_returns_xts_rebalanced_monthly <- 
  Return.portfolio(asset_returns_xts, weights = w, rebalance_on = "months") %>%
  `colnames<-`("returns") 

asset_returns_long <-  
  prices %>% 
  to.monthly(indexAt = "last", OHLC = FALSE) %>% 
  tk_tbl(preserve_index = TRUE, rename_index = "date") %>%
  gather(asset, returns, -date) %>% 
  group_by(asset) %>%  
  mutate(returns = (log(returns) - log(lag(returns)))) %>% 
  na.omit()

portfolio_returns_tq_rebalanced_monthly <- 
  asset_returns_long %>%
  tq_portfolio(assets_col  = asset, 
               returns_col = returns,
               weights     = w,
               col_rename  = "returns",
               rebalance_on = "months")
```

Here, I'm going to use SPY ETF as the baseline of market return, effectively treating the S&P 500 as the market. Let's calculate our market return for SPY and save it as <code>market_return_xts</code>. 

```{r}
spy_monthly_xts <- 
    getSymbols("SPY", 
               src = 'yahoo', 
               from = "2013-01-01", 
               to = "2017-12-31",
             auto.assign = TRUE, 
             warnings = FALSE) %>% 
    map(~Ad(get(.))) %>% 
    reduce(merge) %>%
    `colnames<-`("SPY") %>% 
    to.monthly(indexAt = "last", OHLC = FALSE)

market_returns_xts <-
  Return.calculate(spy_monthly_xts, method = "log") %>% 
  na.omit()
```

I will also need a <code>data.frame</code> object of market returns, and will convert the <code>xts</code> object using <code>tk_tbl(preserve_index = TRUE, rename_index = "date") from the timetk package.

```{r}
market_returns_tidy <-
  market_returns_xts %>% tk_tbl(preserve_index = TRUE, rename_index = "date") %>% na.omit() %>% select(date, returns = SPY)

head(market_returns_tidy)

```

```{r}
portfolio_returns_tq_rebalanced_monthly %>% mutate(market_returns = market_returns_tidy$returns) %>% head()
```

Since above code doesn't throw any error message, we can assuem that portfolio data perfectly align with our market return data.

following is the code and equation to calculate CAPM beta

<code>$${\beta}_{portfolio} = cov(R_p, R_m)/\sigma_m $$</code>

$${\beta}_{portfolio} = cov(R_p, R_m)/\sigma_m $$