---
title: "Calculating Capital Asset Pricing Model"
author: "Eric Wang"
date: "5 March 2018"
output: html_document
---


The portfolio that I'm going to analysis consists:

>+ SPY (S&P500 fund) weighted 25%
>+ EFA (a non-US equities fund) weighted 25%
>+ IJS (a small-cap value fund) weighted 20%
>+ EEM (an emerging-mkts fund) weighted 20%
>+ AGG (a bond fund) weighted 10%

Then I need to find out the monthly returns of above mentioned portfolio, I copied code from <a href = "https://rviews.rstudio.com/2018/02/08/capm-beta/" title="portfolio monthly return">Monthly return</a>

```{r}
library(tidyquant)
library(tidyverse)
library(timetk)
library(tibbletime)
library(broom)

symbols <- c("SPY","EFA", "IJS", "EEM","AGG")

prices <- 
  getSymbols(symbols, src = 'yahoo', 
             from = "2013-01-01",
             to = "2017-12-31",
             auto.assign = TRUE, warnings = FALSE) %>% 
  map(~Ad(get(.))) %>%
  reduce(merge) %>% 
  `colnames<-`(symbols)

prices_monthly <- to.monthly(prices, indexAt = "last", OHLC = FALSE)

asset_returns_xts <- na.omit(Return.calculate(prices_monthly, method = "log"))

w <- c(0.25, 0.25, 0.20, 0.20, 0.10)

portfolio_returns_xts_rebalanced_monthly <- 
  Return.portfolio(asset_returns_xts, weights = w, rebalance_on = "months") %>%
  `colnames<-`("returns") 

asset_returns_long <-  
  prices %>% 
  to.monthly(indexAt = "last", OHLC = FALSE) %>% 
  tk_tbl(preserve_index = TRUE, rename_index = "date") %>%
  gather(asset, returns, -date) %>% 
  group_by(asset) %>%  
  mutate(returns = (log(returns) - log(lag(returns)))) %>% 
  na.omit()

portfolio_returns_tq_rebalanced_monthly <- 
  asset_returns_long %>%
  tq_portfolio(assets_col  = asset, 
               returns_col = returns,
               weights     = w,
               col_rename  = "returns",
               rebalance_on = "months")
```

Here, I'm going to use SPY ETF as the baseline of market return, effectively treating the S&P 500 as the market. Let's calculate our market return for SPY and save it as <code>market_return_xts</code>. 

```{r}
spy_monthly_xts <- 
    getSymbols("SPY", 
               src = 'yahoo', 
               from = "2013-01-01", 
               to = "2017-12-31",
             auto.assign = TRUE, 
             warnings = FALSE) %>% 
    map(~Ad(get(.))) %>% 
    reduce(merge) %>%
    `colnames<-`("SPY") %>% 
    to.monthly(indexAt = "last", OHLC = FALSE)

market_returns_xts <-
  Return.calculate(spy_monthly_xts, method = "log") %>% 
  na.omit()
```

I will also need a <code>data.frame</code> object of market returns, and will convert the <code>xts</code> object using <code>tk_tbl(preserve_index = TRUE, rename_index = "date") from the timetk package.

```{r}
market_returns_tidy <-
  market_returns_xts %>% tk_tbl(preserve_index = TRUE, rename_index = "date") %>% na.omit() %>% select(date, returns = SPY)

head(market_returns_tidy)

```

```{r}
portfolio_returns_tq_rebalanced_monthly %>% mutate(market_returns = market_returns_tidy$returns) %>% head()
```

Since above code doesn't throw any error message, we can assuem that portfolio data perfectly align with our market return data.

following is the code and equation to calculate CAPM beta

<code>$${\beta}_{portfolio} = cov(R_p, R_m)/\sigma_m $$</code>

$${\beta}_{portfolio} = cov(R_p, R_m)/\sigma_m $$

Portfolio beta is equals to the covariance of the portfolio returns and market returns, divided by the variance of market returns. 

Hence, our portfolio beta can be calculated as:

<code>cov(portfolio_returns_xts_rebalanced_monthly, market_returns_tidy$returns)/var(market_returns_tidy$returns)</code>

```{r}
cov(portfolio_returns_xts_rebalanced_monthly, market_returns_tidy$returns)/var(market_returns_tidy$returns)
```

The beta is close to 1 which is as expected since we are using SPY itself as a baseline for the market return, which is also has a big proportion in our portfolio. 

Accroding to this site: https://www.investopedia.com/articles/01/102401.asp

Here ae the possible values and the corrresponding interpretation of beta:

>- Negative beta - A beta less than 0, which would indicate an inverse relation to the market - is possible but highly unlikely. However, some investors believe that gold and gold stocks should have negative betas because they tended to do better when the stock market declines.
- Beta of 0 - Basically, cash has a beta of 0. In other words, regardless of which way the market moves, the value of cash remains unchanged (given no inflation).
Beta between 0 and 1 - Companies with volatilities lower than the market have a beta of less than 1 (but more than 0). As we mentioned earlier, many utilities fall in this range.
- Beta of 1 - A beta of 1 represents the volatility of the given index used to represent the overall market, against which other stocks and their betas are measured. The S&P 500 is such an index. If a stock has a beta of one, it will move the same amount and direction as the index. So, an index fund that mirrors the S&P 500 will have a beta close to 1.
Beta greater than 1 - This denotes a volatility that is greater than the broad-based index. Again, as we mentioned above, many technology companies on the Nasdaq have a beta higher than 1.
- Beta greater than 100 - This is impossible as it essentially denotes a volatility that is 100 times greater than the market. If a stock had a beta of 100, it would be expected to go to 0 on any decline in the stock market. If you ever see a beta of over 100 on a research site it is usually the result of a statistical error, or the given stock has experienced large swings due to low liquidity, such as an over-the-counter stock. For the most part, stocks of well-known companies rarely ever have a beta higher than 

Another way to calculate beta is to calculate beta for each individual asset and multiplying by asset weights. Here is the equation: <code>$${\beta}_{portfolio} ={\sum_{i=1}^n}W _i~{\beta}_i $$</code>

$${\beta}_{portfolio} ={\sum_{i=1}^n}W _i~{\beta}_i $$

We need to regress of our individual asset returns on the market return. We can do <code>lm(asset_return_1 ~ market_returns_tidy$return)</code>, and then do asset_return_2 ... but to be more efficient, we can use <code>map()</code) function to regress all of our assets and calculate betas with one call. 

We will start with our <code>asset_returns_long</code> tidy data frame and will then run nest<code>(~asset)</code>

```{r}
beta_assets <-
  asset_returns_long %>% 
  na.omit() %>%
  nest(-asset)

beta_assets
```

Now all asset returns are nested in one column of the corresponding asset name, hence we can use <code>map()</code> to apply a function to each of these nested lists and store the results in a new column via the <code>mutate(),/code> function. The whole piped command is <code>mutate(model = map(data, ~ lm(returns ~ market_returns_tidy$returns, data = .)))</code>

```{r}
beta_assets <-
  asset_returns_long %>% 
  na.omit() %>% 
  nest(-asset) %>%
  mutate(model = map(data, ~ lm(returns ~ market_returns_tidy$returns, data = .)))

beta_assets
```

We can then tidy our results by using <code>tidy()</code> from <code>broom</code> package. Following call will be used <code>mutate(model = map(model, tidy))</code>

```{r}
beta_assets <-
  asset_returns_long %>%
  na.omit() %>%
  nest(-asset) %>%
  mutate(model = map(data, ~ lm(returns ~ market_returns_tidy$returns, data = .))) %>%
  mutate(model = map(model, tidy))

beta_assets
```

Let's unnest the model data frame

```{r}
beta_assets <-
  asset_returns_long %>%
  na.omit() %>%
  nest(-asset) %>%
  mutate(model = map(data, ~ lm(returns ~ market_returns_tidy$returns, data = .))) %>% 
  mutate(model = map(model, tidy)) %>%
  unnest(model)

beta_assets
```

and we are going to remove the intercept

```{r}
beta_assets <- 
  asset_returns_long %>%
  na.omit() %>% 
  nest(-asset) %>%
  mutate(model = map(data, ~lm(returns ~ market_returns_tidy$returns, data = .))) %>%
  mutate(model = map(model, tidy)) %>%
  unnest(model) %>%
  filter(term == "market_returns_tidy$returns") %>%
  select(-term)

beta_assets
```

A sanity check on the asset beta should reveal that SPY has beta of 1

```{r}
beta_assets %>% select(asset, estimate) %>% filter(asset == "SPY")
```

Let's weight each portfolio's beta by their proportion

```{r}
w <- c(0.25, 0.25, 0.20, 0.20, 0.10)

beta_byhand <- 
  w[1] * beta_assets$estimate[1] + 
  w[2] * beta_assets$estimate[2] + 
  w[3] * beta_assets$estimate[3] +
  w[4] * beta_assets$estimate[4] +
  w[5] * beta_assets$estimate[5]

beta_byhand

```

```{r}
data.frame(c(beta_auto, beta_byhand), row.names = c("auto", "byhand"))
```

Following we are going to calculate beta in both <code>dplyr</code> and <code>tidyquant</code> world.

